---
title: "STA 380 Exercises"
author: "Jocelyne Walker"
date: "08/17/2020"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Visual story telling part 1: green buildings

Predicting expected profitability is essential for investments, especially large capital projects like a $100M 250,000 sq.ft. mixed-use building. From the initial analysis, it appears that the 5% expected premium for green certification is a good investment, as costs may be recovered in less than 8 years. 

```{r 1.1, echo = FALSE, warning = FALSE, message = FALSE}
library(readr)
library(knitr)
library(ggplot2)
library(gridExtra)
library(mosaic)
library(MatchIt)
library(cowplot)
library(corrplot)
options(scipen=999)

file <- "https://raw.githubusercontent.com/jgscott/STA380/master/data/greenbuildings.csv"
green <- read_csv(file)

# Drop those with leasing rates < 10%
green = green[green$leasing_rate >= 10,]

# Define revenue per square foot measure
green$RevPSF = green$Rent * green$leasing_rate / 100

ggplot(green, aes(x = as.factor(green_rating), y = RevPSF), fill = green_rating) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Revenue per Square Foot") +
  labs(title = "Comparing Revenue per Square Foot of Not Green v Green Buildings") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  coord_flip() +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red")
```

We see from the graph above that the medians (black lines on the boxplots) and means (represented by the red stars) of green and non-green building revenue per square foot are different. The not green buildings have a mean of \$24.50, while the green buildings have a mean of \$27.00. This shows that from both means and medians, there is additional revenue on average for green buildings.  

However, there are a number of issues with the original staff member's analysis: 

* The staff member used the median in his analysis rather than the mean. While he is correct that the median is more robust to outliers, it is important to consider outliers in this analysis. Thus, the mean is a better measure of spread for comparing the two groups, and the **treatment of outliers** should be considered in more detail.

* Green and non-green buildings are **inherently different.** Green buildings are more likely to be newer, bigger, Class A developments. Variables like age, size, and class of the building are confounding variables that impact both whether or not a building is green and its revenue per square foot. Because these building groups have confounding variables, we cannot simply compare their means.

* We must consider the **time value of money.** Performing an NPV analysis and talking to the construction company about reducing the cost of the project will supplement our analysis. 

First, instead of dropping all buildings with leasing rates less than 10%, we chose to drop only those with leasing rates less than 1% to consider more of the outliers. 

**What variables appear to be confounding?** 

First, I built a correlation matrix to identify how each of the building predictors are related. 

* We see that a building's Green Rating is slightly positively correlated with Class A, more desirable buildings and negatively correlated with Age. 

* Building Revenue per Square Foot, Rent, and Cluster Rent are all positively correlated. This makes sense as buildings with a higher rent per square foot should have a higher revenue per square foot. Cluster rent and rent tend to be positively correlated as well, as buildings will have similar rents to other buildings in their local markets.  

```{r 1.1.0, echo = FALSE, warning = FALSE, message = FALSE}
green <- read_csv(file)

# Drop those with leasing rates < 10%
green = green[green$leasing_rate >= 10,]

# Define revenue per square foot measure
green$RevPSF = green$Rent * green$leasing_rate / 100
green$empl_gr = as.numeric(green$empl_gr)

corrplot(cor(green), type = "upper", tl.col = "black", tl.srt = 90, p.mat = green$P, sig.level = 0.01, insig = "blank",number.cex=1, tl.cex = 0.75)
```

I then compared boxplots of each of the predictor variables for Not Green versus Green buildings, and the charts for the predictors that may be confounding variables are shown below. 

```{r 1.1.a, echo = FALSE, warning = FALSE, message = FALSE}
green <- read_csv(file)
# Drop those with leasing rates < 1%
green = green[green$leasing_rate >= 1,]

# Define revenue per square foot measure
green$RevPSF = green$Rent * green$leasing_rate / 100

p1 = ggplot(green, aes(x = as.factor(green_rating), y = size)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Size") +
  labs(title = "Size") +
  scale_y_continuous(labels = function(x) format(x, scientific = TRUE)) +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

p2 = ggplot(green, aes(x = as.factor(green_rating), y = empl_gr)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Employment Growth Rate") +
  labs(title = "Comparing Employment Growth Rate of Not Green versus Green Buildings") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

p3 = ggplot(green, aes(x = as.factor(green_rating), y = Rent)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Rent") +
  labs(title = "Comparing Rent of Not Green versus Green Buildings") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

p4 = ggplot(green, aes(x = as.factor(green_rating), y = leasing_rate)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Leasing Rate") +
  labs(title = "Comparing Leasing Rate of Not Green versus Green Buildings") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

p5 = ggplot(green, aes(x = as.factor(green_rating), y = stories)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Stories") +
  labs(title = "Comparing Stories of Not Green versus Green Buildings") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

p6 = ggplot(green, aes(x = as.factor(green_rating), y = age)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Age") +
  labs(title = "Age") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

p7 = ggplot(green, aes(x = as.factor(green_rating), y = renovated)) + 
  geom_boxplot() + 
  xlab("Renovated") +
  labs(title = "Renovations") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

p8 = ggplot(green, aes(x = as.factor(green_rating), y = class_a)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Class A") +
  labs(title = "Class A") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

p9 = ggplot(green, aes(x = as.factor(green_rating), y = class_b)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Class B") +
  labs(title = "Class B") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

p10 = ggplot(green, aes(x = as.factor(green_rating), y = net)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Net") +
  labs(title = "Comparing Net Contract Basis of Not Green versus Green Buildings") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

p11 = ggplot(green, aes(x = as.factor(green_rating), y = amenities)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Amenities") +
  labs(title = "Amenities") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

p12 = ggplot(green, aes(x = as.factor(green_rating), y = cd_total_07)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Cooling Degree Days") +
  labs(title = "Cooling DD") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

p13 = ggplot(green, aes(x = as.factor(green_rating), y = hd_total07)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Heating Degree Days") +
  labs(title = "Heating DD") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

p14 = ggplot(green, aes(x = as.factor(green_rating), y = total_dd_07)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Total Degree Days") +
  labs(title = "Total DD") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

p15 = ggplot(green, aes(x = as.factor(green_rating), y = Precipitation)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Precipitation") +
  labs(title = "Precipiation") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

p16 = ggplot(green, aes(x = as.factor(green_rating), y = Gas_Costs)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Gas Costs") +
  labs(title = "Comparing Gas Costs in Region of Not Green versus Green Buildings") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

p17 = ggplot(green, aes(x = as.factor(green_rating), y = Electricity_Costs)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Electricity Costs") +
  labs(title = "Comparing Electricity Costs in Region of Not Green versus Green Buildings") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

p18 = ggplot(green, aes(x = as.factor(green_rating), y = cluster_rent)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Cluster Rent") +
  labs(title = "Comparing Cluster Rent of Not Green versus Green Buildings") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

plot_grid(p1, p6, p7, p11, p8, p9, p12, p13, nrow = 2, label_size = 2)
```

* Green Buildings tend to be **larger in size** and **younger in age** on average. 

* Green Buildings are also **less likely to have been renovated** and **have more amenities.** 

* Green Buildings are more likely to be **Class A** buildings, the highest quality properties, while Not Green Buildings are more likely to be the lower **Class B** buildings. 

* Green Buildings more often situated in warmer climates that have **higher cooling degree days** and fewer **heating degree days.** 

**So, is the increased Revenue Per Square Foot in Green buildings *really* due to their Green Rating?** Or, instead, is it because they are newer, larger, more desirable buildings that just happen to be green certified? To answer this question, we must "adjust" for these confounding variables in order to compare buildings where the *only difference* is a green certification. 

Theoretically, to answer this developer's question about the economic impact of "going green," we'd like to have two identical 250,000 square foot buildings on East Cesar Chavez: one Green Rated and one Not Green Rated. Only then could we assess whether the 5% expected premium for green certification would hold true. However, we can't do this in East Austin. Instead, we *can* **match our data in order to balance the green and non-green building groups.** 

The goal of our analysis is to adjust for those 8 confounding variables described above like age, size, and class. The matching process entails:

* For each green building, finding a non-green building that is very similar in confounding variables. For example, they have similar ages, stories, and amenities. 

* Pairing the data up into a new dataset so each green building has a “matched” non-green building. 

The output below shows the summary of the matched and unmatched datasets. 

```{r 1.1.b, echo = FALSE, warning = FALSE, message = FALSE}
library(MatchIt)

set.seed(1234)
green_cl = green[complete.cases(green), ]

set.seed(1234)
mymatch = matchit(green_rating ~ size + age + class_a + class_b + renovated + amenities +
                    cd_total_07 + hd_total07, data = green_cl)
summary(mymatch)
green_matched = match.data(mymatch)

a1 = ggplot(green_matched, aes(x = as.factor(green_rating), y = size)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Size") +
  labs(title = "Size") +
  scale_y_continuous(labels = function(x) format(x, scientific = TRUE)) +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

a2 = ggplot(green_matched, aes(x = as.factor(green_rating), y = empl_gr)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Employment Growth Rate") +
  labs(title = "Comparing Employment Growth Rate of Not Green versus Green Buildings") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

a3 = ggplot(green_matched, aes(x = as.factor(green_rating), y = Rent)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Rent") +
  labs(title = "Comparing Rent of Not Green versus Green Buildings") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

a4 = ggplot(green_matched, aes(x = as.factor(green_rating), y = leasing_rate)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Leasing Rate") +
  labs(title = "Comparing Leasing Rate of Not Green versus Green Buildings") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

a5 = ggplot(green_matched, aes(x = as.factor(green_rating), y = stories)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Stories") +
  labs(title = "Comparing Stories of Not Green versus Green Buildings") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

a6 = ggplot(green_matched, aes(x = as.factor(green_rating), y = age)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Age") +
  labs(title = "Age") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

a7 = ggplot(green_matched, aes(x = as.factor(green_rating), y = renovated)) + 
  geom_boxplot() + 
  xlab("Renovated") +
  labs(title = "Renovations") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 


a8 = ggplot(green_matched, aes(x = as.factor(green_rating), y = class_a)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Class A") +
  labs(title = "Class A") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

a9 = ggplot(green_matched, aes(x = as.factor(green_rating), y = class_b)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Class B") +
  labs(title = "Class B") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

a10 = ggplot(green_matched, aes(x = as.factor(green_rating), y = net)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Net") +
  labs(title = "Comparing Net Contract Basis of Not Green versus Green Buildings") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

a11 = ggplot(green_matched, aes(x = as.factor(green_rating), y = amenities)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Amenities") +
  labs(title = "Amenities") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

a12 = ggplot(green_matched, aes(x = as.factor(green_rating), y = cd_total_07)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Cooling Degree Days") +
  labs(title = "Cooling DD") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

a13 = ggplot(green_matched, aes(x = as.factor(green_rating), y = hd_total07)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Heating Degree Days") +
  labs(title = "Heating DD") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

a14 = ggplot(green_matched, aes(x = as.factor(green_rating), y = total_dd_07)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Total Degree Days") +
  labs(title = "Total DD") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

a15 = ggplot(green_matched, aes(x = as.factor(green_rating), y = Precipitation)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Precipitation") +
  labs(title = "Precipiation") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

a16 = ggplot(green_matched, aes(x = as.factor(green_rating), y = Gas_Costs)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Gas Costs") +
  labs(title = "Comparing Gas Costs in Region of Not Green versus Green Buildings") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

a17 = ggplot(green_matched, aes(x = as.factor(green_rating), y = Electricity_Costs)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Electricity Costs") +
  labs(title = "Comparing Electricity Costs in Region of Not Green versus Green Buildings") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 

a18 = ggplot(green_matched, aes(x = as.factor(green_rating), y = cluster_rent)) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Cluster Rent") +
  labs(title = "Comparing Cluster Rent of Not Green versus Green Buildings") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red") 
```

The graphs below represent the compared boxplots of the data *before* matching and the data *after* matching. Each left graph is before matching, and each graph on the right shows the difference in the matched data. There is now much smaller difference in confounding variables. 

```{r 1.1.c, echo = FALSE, warning = FALSE, message = FALSE}
plot_grid(p1,a1, p6,a6, p7,a7, p11,a11, nrow = 2, label_size = 2, scale = 1)
plot_grid(p8,a8, p9,a9, p12,a12, p13,a13, nrow = 2, label_size = 2, scale = 1)

set.seed(1234)
#mean(RevPSF ~ green_rating, data= green_matched)

ggplot(green_matched, aes(x = as.factor(green_rating), y = RevPSF), fill = green_rating) + 
  geom_boxplot() + 
  xlab("Green Rating") + 
  ylab("Revenue per Square Foot") +
  labs(title = "Comparing Revenue per Square Foot of Matched Buildings") +
  scale_x_discrete(labels = c("Not Green", "Green")) +
  coord_flip() +
  stat_summary(aes(label=round(..y..,2)), fun.y = "mean", geom = "point", shape = 8, size = 2, color = "red")

```

Balancing the data allows me to compare like with like. This eliminates the effect of the confounding variables because now the confounders are equal between the two different groups. It is now reasonable to compare the Revenue per Square Foot of Green and Non-Green buildings and make a conclusion about the impact of green rating because green rating is the only thing that is different between the two groups. 

This is a better approach because we know that green rating is the only variable that is impacting differences in revenue per square foot. In the first situation, the differences in groups could have been caused by a number of confounding variables. 

**Now that we've adjusted for confounding variables, the differences in mean revenue in the matched groups are smaller.** The mean revenue per square foot of the **non-green  matched buildings is \$26.24**, while the **mean of the green buildings is \$26.97**, resulting in a difference of **$0.73** per square foot. This is much smaller than original estimate of \$2.60 increased revenue per square foot. This would translate into an additional 250,000 * 0.73 = \$182,500 of extra revenue per year. If the expected baseline construction costs are \$100 million, with an expected 5% premium for green certification, that means we should expect to spend an extra \$5 million on the green building. It would take 5,000,000/182,500 = 27.4 years to recuperate the costs, without accounting for the time value of money. **This does not seem like a good financial move to build the green building; it is much riskier than the original estimate.**

**Next, we need to estimate how "stable" our estimate of $0.77 increased revenue per square foot of a green building is.** We ran a bootstrapped linear model to understand how the coefficient for **green rating** changes as we resample with replacement. The histogram of these coefficients is shown below, and the 95% confidence interval for the coefficient for green rating is -\$1.18 to +\$1.91 with a mean of \$0.46 per square foot. 

```{r 1.b.1, echo=FALSE, warning = FALSE, message = FALSE}
set.seed(1234)
boot_lm = do(2500)*{
  lm_boot = lm(RevPSF ~ green_rating + size + age + class_a + class_b + renovated + amenities +
                    cd_total_07 + hd_total07, data = resample(green_matched))
}
hist(boot_lm$green_rating, main = "Impact of Green Rating on Revenue per Square Foot", xlab = "Green Rating Coefficient")
```

From the bootstrapped regression, our estimate for the coefficient of green rating falls again, and we are not sure that it is greater than 0, as 0 is included in the confidence interval. This shows that there's **no significant difference** in rental revenue between green and not-green buildings, and the green construction certification is not a profitable investment. 

The upper 95% confidence interval is \$1.91 Revenue per Square Foot. Assuming a lift at the 95% coefficient level, 6% discount rate, and 90% leasing rate for the next 30 years, the NPV of this investment is \$915,436.

Assuming the mean coefficient of \$0.46, 6% discount rate, and 90% leasing rate for the next 30 years, the **NPV of this investment is -\$3,575,340.** This negative NPV shows that this is not a profitable investment, and **the \$5,000,000 could be better spent on more development space or amenities that may be more likely to increase revenue per square foot.** 

```{r 1.b.2, echo=FALSE, warning = FALSE, message = FALSE}
library(FinancialMath)
cf = c(rep(1.91*250000*.9,30))
years = c(1:30)
#NPV(-5000000,cf,times =years,i=0.06)

cf = c(rep(0.46*250000*.9,30))
years = c(1:30)
#NPV(-5000000,cf,times =years,i=0.06)
```


## Visual story telling part 2: flights at ABIA

```{r 2.1, echo=FALSE, warning = FALSE, message = FALSE}
file <- "https://raw.githubusercontent.com/jgscott/STA380/master/data/ABIA.csv"
abia <- read_csv(file)
```

## Portfolio Modeling

```{r 3.1, echo=FALSE, warning = FALSE, message = FALSE}

```

## Market segmentation

```{r 4.1, echo=FALSE, warning = FALSE, message = FALSE}
file <- "https://raw.githubusercontent.com/jgscott/STA380/master/data/social_marketing.csv"
social <- read_csv(file)


```

## Author attribution

```{r 5.1, echo=FALSE, warning = FALSE, message = FALSE}

```

## Association rule mining

```{r 6.1, echo=FALSE, warning = FALSE, message = FALSE}
#file <- "https://raw.githubusercontent.com/jgscott/STA380/master/data/groceries.txt"


```